---
title: "Plot jacknife: AN vs BE BROAD"
author: "Abigail ter Kuile & Helena Davies"
date: "2022-12-22"
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

```{r load packages}
library(summarytools)
library(skimr)
library(gtsummary)
#library(ggview)
library(patchwork)
library(tidyverse)
```

# Read in & transform data
Trait 1
```{r Read in the data trait 1}
rgs_AN_non_MVP <- read_csv(file = "/Users/helenadavies/werk/PGC_ED_Freeze3/PGC_ED_F3_github_scripts/secondary_analysis_rg_results/AN_PGCED3_rgs.csv")
                             
rgs_AN_non_MVP
```

# Keep correct traits in rg
```{r keep correct traits}
rgs_AN_non_MVP <- rgs_AN_non_MVP %>% 
  filter(p2 == "ADHD06" |
           p2 == "SMOK10" |
           p2 == "ALCD03" |
           p2 == "ALCU01" |
           p2 == "ALCU02" |
           p2 == "ALCU03" |
           p2 == "ALZH01" |
           p2 == "ANOR02" |
           p2 == "ANOR03" |
           p2 == "ANXI03" |
           p2 == "ASTH01" |
           p2 == "AUTI07" |
           p2 == "BALD01" |
           p2 == "BFPC03" |
           p2 == "BIPO03" |
           p2 == "BIPO04" |
           p2 == "BIPO05" |
           p2 == "BLOO01" |
           p2 == "BLOO02" |
           p2 == "BLOO03" |
           p2 == "BLOO04" |
           p2 == "BLOO05" |
           p2 == "BLOO06" |
           p2 == "BLOO07" |
           p2 == "BLOO08" |
           p2 == "BLOO09" |
           p2 == "BLOO10" |
           p2 == "BLOO11" |
           p2 == "BLOO12" |
           p2 == "BLOO13" |
           p2 == "BLOO14" |
           p2 == "BLOO15" |
           p2 == "BLOO16" |
           p2 == "BLOO17" |
           p2 == "BLOO18" |
           p2 == "BLOO19" |
           p2 == "BLOO20" |
           p2 == "BLOO21" |
           p2 == "BLOO22" |
           p2 == "BLOO23" |
           p2 == "BLOO24" |
           p2 == "BLOO25" |
           p2 == "BLOO26" |
           p2 == "BLOO27" |
           p2 == "BLOO28" |
           p2 == "BLOO29" |
           p2 == "BLOO30" |
           p2 == "BLOO31" |
           p2 == "BLOO32" |
           p2 == "BLOO33" |
           p2 == "BLOO34" |
           p2 == "BLOO35" |
           p2 == "BLOO36" |
           p2 == "BODY02" |
           p2 == "BODY04" |
           p2 == "BODY07" |
           p2 == "CANU02" |
           p2 == "CANU03" |
           p2 == "CAUD01" |
           p2 == "CELI01" |
           p2 == "CHOL21" |
           p2 == "CHOL22" |
           p2 == "CHOL27" |
           p2 == "CHRO01" |
           p2 == "CHRO02" |
           p2 == "CHRO06" |
           p2 == "SMOK09" |
           p2 == "CIRR01" |
           p2 == "COAD03" |
           p2 == "COLL01" |
           p2 == "CROH01" |
           p2 == "CROS01" |
           p2 == "DEPR02" |
           p2 == "DEPR05" |
           p2 == "DIAB02" |
           p2 == "ALCO04" |
           p2 == "EDUC02" |
           p2 == "EXTR01" |
           p2 == "FATM02" |
           p2 == "FATM02B" |
           p2 == "FATM02F" |
           p2 == "FATM02M" |
           p2 == "FATM03" |
           p2 == "FATM03B" |
           p2 == "FATM03F" |
           p2 == "FATM03M" |
           p2 == "FATM04" |
           p2 == "FATM04B" |
           p2 == "FATM04F" |
           p2 == "FATM04M" |
           p2 == "FATM05B" |
           p2 == "ANXI04" |
           p2 == "GLYC02" |
           p2 == "GLYC04" |
           p2 == "GLYC05" |
           p2 == "GLYC07" |
           p2 == "GLYC08" |
           p2 == "GLYC13" |
           p2 == "GLYC14" |
           p2 == "GLYC16" |
           p2 == "GLYC22" |
           p2 == "GROW01" |
           p2 == "GROW01F" |
           p2 == "GROW03" |
           p2 == "HEAD01" |
           p2 == "HEAL01" |
           p2 == "HEAR01" |
           p2 == "HEIG01" |
           p2 == "HEIG02" |
           p2 == "HEIG07" |
         #  p2 == "HEIG08" | using updated HEIG09
           p2 == "HIPC01" |
           p2 == "HIPC01F" |
           p2 == "HIPC01M" |
           p2 == "HIPC03" |
           p2 == "HIPC03F" |
           p2 == "HIPC03M" |
           p2 == "INCO01" |
           p2 == "INCO03" |
           p2 == "INFB01" | 
         #  p2 == "INSO02" | using updated INSO03
           p2 == "INTE01" |
           p2 == "INTE03" |
           p2 == "LEAN02" |
           p2 == "LEAN03" |
           p2 == "LEAN04" |
           p2 == "LEAN04B" |
           p2 == "LEAN04F" |
           p2 == "LEAN04M" |
           p2 == "LEAN05" |
           p2 == "LEAN05B" |
           p2 == "LEAN05F" |
           p2 == "LEAN05M" |
           p2 == "LEAN06" |
           p2 == "LEAN06B" |
           p2 == "LEAN06F" |
           p2 == "LEAN06M" |
           p2 == "LEAN07B" |
           p2 == "LONG01" |
           p2 == "LONG02" |
           p2 == "LONG03" |
           p2 == "LONG04" |
           p2 == "LONG05" |
           p2 == "LONG06" |
           p2 == "LONG07" |
           p2 == "LUNG01" |
           p2 == "LUNG02" |
           p2 == "LUNG03" |
           p2 == "LUNG05" |
           p2 == "LUPU01" |
           p2 == "MEMO01" |
           p2 == "MENA03F" |
           p2 == "MENO01F" |
           p2 == "MIGR01" |
           p2 == "NEUR02B" |
           p2 == "OBES01" |
           p2 == "OBES02" |
           p2 == "OBES03" |
           p2 == "OBES05" |
           p2 == "OBES07" |
           p2 == "OCDI01" |
           p2 == "OSTE01" |
           p2 == "OSTE03" |
           p2 == "OSTE04" |
           p2 == "OSTE05" |
           p2 == "OVER01" |
           p2 == "ANXI05" |
           p2 == "PHYS01" |
           p2 == "PRCA01" |
           p2 == "PUTA01" |
           p2 == "REAC01" |
           p2 == "REAS01" |
           p2 == "REPR01" |
           p2 == "REPR01F" |
           p2 == "REPR01M" |
           p2 == "REPR02" |
           p2 == "REPR02F" |
           p2 == "REPR02M" |
           p2 == "RHEU02" |
           p2 == "RISK01" |
           p2 == "RISK02" |
           p2 == "RISK03" |
           p2 == "SCBP01" |
           p2 == "SCBP02" |
           p2 == "SCHI05" |
           p2 == "SMOK05" |
           p2 == "SMOK08" |
           p2 == "SMOK07" |
           p2 == "SUBJ01" |
           p2 == "THIN01" |
           p2 == "TIRE01" |
           p2 == "TOUR01" |
           p2 == "TRGL04" |
           p2 == "URAT01" |
           p2 == "URIN08" |
           p2 == "URIN11" |
           p2 == "VITD01" |
           p2 == "WAIS01F" |
           p2 == "WAIS01M" |
           p2 == "WAIS03" |
           p2 == "WAIS03F" |
           p2 == "WAIS03M" |
           p2 == "WEIG01" |
           p2 == "WEIG04F" |
           p2 == "WEIG04M" |
           p2 == "WEIG05F" |
           p2 == "WHIP01" |
           p2 == "WHIP03" |
           p2 == "WHIP03F" |
           p2 == "WHIP03M" |
           p2 == "WHIP05" |
           p2 == "WHIP05F" |
           p2 == "WHIP05M" |
           p2 == "BODY04F" |
           p2 == "BODY04M" |
           p2 == "EDUC03" |
           p2 == "HEIG09" |
           p2 == "CROS01" |
           p2 == "PSOR01" |
           p2 == "SMOK11" |
           p2 == "INSO03" |
           p2 == "ADHD06" |
           p2 == "SMOK10" |
           p2 == "BIPO03" |
           p2 == "BIPO04" |
           p2 == "BIPO05" |
           p2 == "CANU02" |
           p2 == "CANU03" |
           p2 == "SMOK09" |
           p2 == "ALCO04" |
           p2 == "SMOK08" |
           p2 == "SMOK07" |
           p2 == "ANXI05" |
           p2 == "TOUR01" |
           p2 == "LONE04" |
           p2 == "BODY15" |
           p2 == "GLYC47" |
           p2 == "GLYC48" |
           p2 == "GLYC49" |
           p2 == "GLYC48F" |
           p2 == "GLYC48M" |
           p2 == "GLYC50" |
           p2 == "GLYC51" |
           p2 == "GLYC50F" |
           p2 == "GLYC50M" |
          # p2 == "GLYC52" | USING glyc22 as bigger h2
           p2 == "GLYC53" |
           p2 == "REPR04" |
           p2 == "REPR03")
```

Trait 1 MVP
```{r Read in the data trait 1 mvp}
rgs_AN_MVP <- read_csv(file = "/Users/helenadavies/werk/PGC_ED_Freeze3/PGC_ED_F3_github_scripts/secondary_analysis_rg_results/AN_PGCED3_MVP_rgs_MVP.csv")
                             
rgs_AN_MVP
```

Bind
```{r bind AN rgs}
rgs_AN <- rgs_AN_non_MVP %>%
  bind_rows(rgs_AN_MVP)
```

Trait 2
```{r Read in the data trait 2}
rgs_BEBROAD_non_MVP <- read_csv(file = "/Users/helenadavies/werk/PGC_ED_Freeze3/PGC_ED_F3_github_scripts/secondary_analysis_rg_results/BEBROAD_PGCED3_rgs.csv")

rgs_BEBROAD_non_MVP
```


# Keep correct traits in rg
```{r keep correct traits}
rgs_BEBROAD_non_MVP <- rgs_BEBROAD_non_MVP %>% 
  filter(p2 == "ADHD06" |
           p2 == "SMOK10" |
           p2 == "ALCD03" |
           p2 == "ALCU01" |
           p2 == "ALCU02" |
           p2 == "ALCU03" |
           p2 == "ALZH01" |
           p2 == "ANOR02" |
           p2 == "ANOR03" |
           p2 == "ANXI03" |
           p2 == "ASTH01" |
           p2 == "AUTI07" |
           p2 == "BALD01" |
           p2 == "BFPC03" |
           p2 == "BIPO03" |
           p2 == "BIPO04" |
           p2 == "BIPO05" |
           p2 == "BLOO01" |
           p2 == "BLOO02" |
           p2 == "BLOO03" |
           p2 == "BLOO04" |
           p2 == "BLOO05" |
           p2 == "BLOO06" |
           p2 == "BLOO07" |
           p2 == "BLOO08" |
           p2 == "BLOO09" |
           p2 == "BLOO10" |
           p2 == "BLOO11" |
           p2 == "BLOO12" |
           p2 == "BLOO13" |
           p2 == "BLOO14" |
           p2 == "BLOO15" |
           p2 == "BLOO16" |
           p2 == "BLOO17" |
           p2 == "BLOO18" |
           p2 == "BLOO19" |
           p2 == "BLOO20" |
           p2 == "BLOO21" |
           p2 == "BLOO22" |
           p2 == "BLOO23" |
           p2 == "BLOO24" |
           p2 == "BLOO25" |
           p2 == "BLOO26" |
           p2 == "BLOO27" |
           p2 == "BLOO28" |
           p2 == "BLOO29" |
           p2 == "BLOO30" |
           p2 == "BLOO31" |
           p2 == "BLOO32" |
           p2 == "BLOO33" |
           p2 == "BLOO34" |
           p2 == "BLOO35" |
           p2 == "BLOO36" |
           p2 == "BODY02" |
           p2 == "BODY04" |
           p2 == "BODY07" |
           p2 == "CANU02" |
           p2 == "CANU03" |
           p2 == "CAUD01" |
           p2 == "CELI01" |
           p2 == "CHOL21" |
           p2 == "CHOL22" |
           p2 == "CHOL27" |
           p2 == "CHRO01" |
           p2 == "CHRO02" |
           p2 == "CHRO06" |
           p2 == "SMOK09" |
           p2 == "CIRR01" |
           p2 == "COAD03" |
           p2 == "COLL01" |
           p2 == "CROH01" |
           p2 == "CROS01" |
           p2 == "DEPR02" |
           p2 == "DEPR05" |
           p2 == "DIAB02" |
           p2 == "ALCO04" |
           p2 == "EDUC02" |
           p2 == "EXTR01" |
           p2 == "FATM02" |
           p2 == "FATM02B" |
           p2 == "FATM02F" |
           p2 == "FATM02M" |
           p2 == "FATM03" |
           p2 == "FATM03B" |
           p2 == "FATM03F" |
           p2 == "FATM03M" |
           p2 == "FATM04" |
           p2 == "FATM04B" |
           p2 == "FATM04F" |
           p2 == "FATM04M" |
           p2 == "FATM05B" |
           p2 == "ANXI04" |
           p2 == "GLYC02" |
           p2 == "GLYC04" |
           p2 == "GLYC05" |
           p2 == "GLYC07" |
           p2 == "GLYC08" |
           p2 == "GLYC13" |
           p2 == "GLYC14" |
           p2 == "GLYC16" |
           p2 == "GLYC22" |
           p2 == "GROW01" |
           p2 == "GROW01F" |
           p2 == "GROW03" |
           p2 == "HEAD01" |
           p2 == "HEAL01" |
           p2 == "HEAR01" |
           p2 == "HEIG01" |
           p2 == "HEIG02" |
           p2 == "HEIG07" |
         #  p2 == "HEIG08" | using updated HEIG09
           p2 == "HIPC01" |
           p2 == "HIPC01F" |
           p2 == "HIPC01M" |
           p2 == "HIPC03" |
           p2 == "HIPC03F" |
           p2 == "HIPC03M" |
           p2 == "INCO01" |
           p2 == "INCO03" |
           p2 == "INFB01" |
         #  p2 == "INSO02" | using updated INSO03
           p2 == "INTE01" |
           p2 == "INTE03" |
           p2 == "LEAN02" |
           p2 == "LEAN03" |
           p2 == "LEAN04" |
           p2 == "LEAN04B" |
           p2 == "LEAN04F" |
           p2 == "LEAN04M" |
           p2 == "LEAN05" |
           p2 == "LEAN05B" |
           p2 == "LEAN05F" |
           p2 == "LEAN05M" |
           p2 == "LEAN06" |
           p2 == "LEAN06B" |
           p2 == "LEAN06F" |
           p2 == "LEAN06M" |
           p2 == "LEAN07B" |
           p2 == "LONG01" |
           p2 == "LONG02" |
           p2 == "LONG03" |
           p2 == "LONG04" |
           p2 == "LONG05" |
           p2 == "LONG06" |
           p2 == "LONG07" |
           p2 == "LUNG01" |
           p2 == "LUNG02" |
           p2 == "LUNG03" |
           p2 == "LUNG05" |
           p2 == "LUPU01" |
           p2 == "MEMO01" |
           p2 == "MENA03F" |
           p2 == "MENO01F" |
           p2 == "MIGR01" |
           p2 == "NEUR02B" |
           p2 == "OBES01" |
           p2 == "OBES02" |
           p2 == "OBES03" |
           p2 == "OBES05" |
           p2 == "OBES07" |
           p2 == "OCDI01" |
           p2 == "OSTE01" |
           p2 == "OSTE03" |
           p2 == "OSTE04" |
           p2 == "OSTE05" |
           p2 == "OVER01" |
           p2 == "ANXI05" |
           p2 == "PHYS01" |
           p2 == "PRCA01" |
           p2 == "PUTA01" |
           p2 == "REAC01" |
           p2 == "REAS01" |
           p2 == "REPR01" |
           p2 == "REPR01F" |
           p2 == "REPR01M" |
           p2 == "REPR02" |
           p2 == "REPR02F" |
           p2 == "REPR02M" |
           p2 == "RHEU02" |
           p2 == "RISK01" |
           p2 == "RISK02" |
           p2 == "RISK03" |
           p2 == "SCBP01" |
           p2 == "SCBP02" |
           p2 == "SCHI05" |
           p2 == "SMOK05" |
           p2 == "SMOK08" |
           p2 == "SMOK07" |
           p2 == "SUBJ01" |
           p2 == "THIN01" |
           p2 == "TIRE01" |
           p2 == "TOUR01" |
           p2 == "TRGL04" |
           p2 == "URAT01" |
           p2 == "URIN08" |
           p2 == "URIN11" |
           p2 == "VITD01" |
           p2 == "WAIS01F" |
           p2 == "WAIS01M" |
           p2 == "WAIS03" |
           p2 == "WAIS03F" |
           p2 == "WAIS03M" |
           p2 == "WEIG01" |
           p2 == "WEIG04F" |
           p2 == "WEIG04M" |
           p2 == "WEIG05F" |
           p2 == "WHIP01" |
           p2 == "WHIP03" |
           p2 == "WHIP03F" |
           p2 == "WHIP03M" |
           p2 == "WHIP05" |
           p2 == "WHIP05F" |
           p2 == "WHIP05M" |
           p2 == "BODY04F" |
           p2 == "BODY04M" |
           p2 == "EDUC03" |
           p2 == "HEIG09" |
           p2 == "CROS01" |
           p2 == "PSOR01" |
           p2 == "SMOK11" |
           p2 == "INSO03" |
           p2 == "ADHD06" |
           p2 == "SMOK10" |
           p2 == "BIPO03" |
           p2 == "BIPO04" |
           p2 == "BIPO05" |
           p2 == "CANU02" |
           p2 == "CANU03" |
           p2 == "SMOK09" |
           p2 == "ALCO04" |
           p2 == "SMOK08" |
           p2 == "SMOK07" |
           p2 == "ANXI05" |
           p2 == "TOUR01" |
           p2 == "LONE04" |
           p2 == "BODY15" |
           p2 == "GLYC47" |
           p2 == "GLYC48" |
           p2 == "GLYC49" |
           p2 == "GLYC48F" |
           p2 == "GLYC48M" |
           p2 == "GLYC50" |
           p2 == "GLYC51" |
           p2 == "GLYC50F" |
           p2 == "GLYC50M" |
          # p2 == "GLYC52" | USING glyc22 as bigger h2
           p2 == "GLYC53" |
           p2 == "REPR04" |
           p2 == "REPR03")
```

Trait 2 MVP
```{r Read in the data trait 2 mvp}
rgs_BEBROAD_MVP <- read_csv(file = "/Users/helenadavies/werk/PGC_ED_Freeze3/PGC_ED_F3_github_scripts/secondary_analysis_rg_results/BEBROAD_PGCED3_MVP_rgs_MVP.csv")
                             
rgs_BEBROAD_MVP
```
Bind
```{r bind AN rgs}
rgs_BEBROAD <- rgs_BEBROAD_non_MVP %>%
  bind_rows(rgs_BEBROAD_MVP)
```

Check overlap in traits, should be the same
```{r check overlap}
#check difference in merging variable Phenotype
AN_traits <- rgs_AN %>% 
  select(p2)

BEBROAD_traits <- rgs_BEBROAD %>% 
  select(p2)

setdiff(rownames(AN_traits), rownames(BEBROAD_traits))
```

Bind the rows of all data frames
```{r Bind the rows of all data frames}
rgs_results <- bind_rows(rgs_BEBROAD,
                 rgs_AN)
# check
if(nrow(rgs_BEBROAD) + nrow(rgs_AN) == nrow(rgs_results)) 
{ print("Binding rows worked!")} else {print("Binding rows didn't work!")}
```
Remove NAs
```{r}
rgs_results <- rgs_results %>%
  filter(!is.na(rg))
```


Merge with GWAS information sheet to get phenotype name for plotting
```{r merge with GWAS info}
trait_details <- read_csv(file = "/Users/helenadavies/Downloads/PGC ED GWAS rg analyses - RULES APPLIED_ PGC-ED rg traits (9).csv")

trait_details <- trait_details %>% 
  select(p2 = "KCL code",
         name,
         name_plotting) # rename Code to p2 so that it matches with column name in rg results

rgs_results_details <- left_join(rgs_results,
                                 trait_details,
                                 by = "p2")

rgs_results_details

## for now ##
rgs_results_details <- rgs_results_details %>%
  mutate(name =
           case_when(!is.na(name_plotting) ~ name_plotting,
                     TRUE ~ name))
```

Merge rows to a single trait, by renaming p value to p_BEBROAD and p_AN - to filter traits that are non-significant for both
```{r merge to single trait}
rgs_BEBROAD_specific_to_filter <- rgs_BEBROAD %>% 
  select(p2,
         p_BEBROAD = p,
         rg_BEBROAD = rg)

rgs_BEBROAD_specific_to_filter

rgs_AN_specific_to_filter <- rgs_AN %>% 
  select(p2,
         p_AN = p,
         rg_AN = rg)

rgs_AN_specific_to_filter

p_BEBROAD_AN <- inner_join(rgs_AN_specific_to_filter,
                           rgs_BEBROAD_specific_to_filter,
                         by = "p2")

p_BEBROAD_AN
```

Set number of traits tested for bonferonni correction 
```{r no. of traits for bonf correction}
n_traits <- nrow(rgs_BEBROAD)
n_traits

Bonf_threshold <- (0.05/n_traits)
Bonf_threshold
```

Create column to specify if significant for AN or BE BROAD
```{r sig for AN or BE BROAD}
p_BEBROAD_AN <- p_BEBROAD_AN %>%
  mutate(bonf_signif =
           case_when((p_AN <= (0.05/n_traits))
                     & (p_BEBROAD <= (0.05/n_traits)) ~ "AN & BE BROAD bonf significant",
                     (p_AN > (0.05/n_traits))
                     & (p_BEBROAD > (0.05/n_traits)) ~ "AN & BE BROAD bonf non-significant",
                     (p_BEBROAD > (0.05/n_traits))
                     & (p_AN <= (0.05/n_traits)) ~ "Only AN bonf significant",
                     (p_AN > (0.05/n_traits))
                     & (p_BEBROAD <= (0.05/n_traits)) ~ "Only BE BROAD bonf significant"))

p_BEBROAD_AN %>%
  freq(bonf_signif)
```

Add variable to say if abs rg is stronger for fear or for gad. This is for plotting blockjacknife results, where the rg is different but significant for both - note this is just stronger in terms of direction (not yet applying if this is significant or not from jackknife results)
```{r direction of strength AN or BE BROAD}
p_BEBROAD_AN <- p_BEBROAD_AN %>%
  mutate(rg_higher_AN_or_BEBROAD =
           case_when(rg_AN > rg_BEBROAD ~ "Higher rg with AN",
                     rg_BEBROAD > rg_AN ~ "Higher rg with BE BROAD"))

p_BEBROAD_AN %>%
  freq(rg_higher_AN_or_BEBROAD)
```

# Merge back with gwas detail info
```{r merge with gwas details}
rg_p_BEBROAD_AN_details <- inner_join(rgs_results_details, 
                                   p_BEBROAD_AN, 
                                   by = "p2")

rg_p_BEBROAD_AN_details
```

# Read in and transform results from block jacknife 
(testing whether two rg's are significantly different from each other)
```{r Read in the jackknife data}
jacknife_results <- data.table::fread(file = "/Users/helenadavies/werk/PGC_ED_Freeze3/PGC_ED_F3_github_scripts/secondary_analysis_rg_results/AN_BEBROAD_jacknife_results2.txt",
                          sep = " ")
                             
jacknife_results <- jacknife_results %>% 
  rename(p2 = phenotype,
         jn_pvalue_diff_0 = 'pvalue(diff!=0)',
         jn_Zvalue_diff_0 ='zscore(diff!=0)')

jacknife_results
```
Check same as rgs
```{r}
jacknife_results_traits <- jacknife_results %>% 
  select(p2)

differences <- setdiff(rownames(AN_traits),
                       rownames(jacknife_results_traits))

diff <- anti_join(AN_traits,
                  jacknife_results_traits)

# Traits in rg not in jackknife
diff
```

```{r filter out NAs}
jacknife_results <- jacknife_results %>%
  filter(!is.na(var))
```

Check overlap in traits, should be the same
```{r check overlap jackknife}
#check difference in merging variable Phenotype
jacknife_results_traits <- jacknife_results %>% 
  select(p2)

setdiff(rownames(jacknife_results_traits), rownames(BEBROAD_traits))
setdiff(rownames(BEBROAD_traits), rownames(jacknife_results_traits))
```

Merge jacknife with rg results and gwas details
```{r merge jackknife and rg and gwas details}
rg_p_BEBROAD_AN_details$se_rg <- rg_p_BEBROAD_AN_details$se

jacknife_rg <- left_join(rg_p_BEBROAD_AN_details,
                         jacknife_results,
                         by = "p2")

jacknife_rg
```

Create column to specify if jackknife significantly different rg results
```{r new column jackknife sig}
jacknife_rg <- jacknife_rg %>%
  mutate(jn_diff =
           case_when((jn_pvalue_diff_0 <= (0.05/n_traits)) ~ "rg jn different",
                     (jn_pvalue_diff_0 > (0.05/n_traits)) ~ "rg jn same"))

jacknife_rg %>% 
  freq(jn_diff)
```

Create variable for plotting
```{r jackknife variable for plotting}
jacknife_rg <- jacknife_rg %>%
  mutate(jn_diff_rg_stronger_AN_or_BEBROAD_plotting = 
           case_when(jn_diff == "rg jn different" 
                        & rg_higher_AN_or_BEBROAD == "Higher rg with BE BROAD" 
                       & bonf_signif != "AN & BE BROAD bonf non-significant" ~ "BEBROAD rg > AN rg",
                     
                     jn_diff == "rg jn different" 
                     & rg_higher_AN_or_BEBROAD == "Higher rg with AN"
                     & bonf_signif != "AN & BE BROAD bonf non-significant" ~ "AN rg > BE BROAD rg",
                     
                     jn_diff == "rg jn same"
                     & bonf_signif == "AN & BE BROAD bonf significant" ~ "Both sig",
                     
                     jn_diff == "rg jn same"
                     & bonf_signif == "Only BE BROAD bonf significant" ~ "Only BE BROAD sig",
                     
                     jn_diff == "rg jn same"
                     & bonf_signif == "Only AN bonf significant" ~ "Only AN sig",
                     
                     bonf_signif == "AN & BE BROAD bonf non-significant" ~ "AN & BE BROAD both non-sig (no jackknife)",
                     
                     TRUE ~ jn_diff
                      ))
                      

jacknife_rg %>% 
  freq(jn_diff_rg_stronger_AN_or_BEBROAD_plotting)
```

Save for supplementary table
```{r save table for supplementary}
supp_jacknife_rg <- jacknife_rg %>%
  filter(!is.na(p1)) %>%
  select(
    Trait = name,
    "rg with BE BROAD" = rg_BEBROAD,
    "p value for BE BROAD rg" = p_BEBROAD,
    "rg with AN" = rg_AN,
    "p value for AN rg" = p_AN,
    bonf_signif,
    "Jackknife results" = jn_diff_rg_stronger_AN_or_BEBROAD_plotting
  ) 
  
supp_jacknife_rg <- supp_jacknife_rg[!duplicated(supp_jacknife_rg$Trait), ]

supp_jacknife_rg %>%
  write_excel_csv(file = "/Users/helenadavies/werk/PGC_ED_Freeze3/PGC_ED_F3_github_scripts/secondary_analysis_rg_results/AN_BEBROAD_PGCED3_rgs_jackknife_SUPPLEMENTARY2.csv")
```

Filter dataframe for plotting: remove traits that are non-significant for both
```{r remove non-sig traits}
jacknife_rg_plotting <- jacknife_rg %>% 
  filter(bonf_signif != "AN & BE BROAD bonf non-significant")

# check 
jacknife_rg_plotting %>% 
  freq(jn_diff_rg_stronger_AN_or_BEBROAD_plotting)
```

## PLotting
Create variables with nice names for plotting
```{r new names for plotting}
jacknife_rg_plotting <- jacknife_rg_plotting %>%
  mutate(bonf_signif_plotting =
           case_when(p1 == "BEBROAD" & p <= (0.05/n_traits) ~ "BEBROAD: significant",
                                        p1 =="BEBROAD" & p > (0.05/n_traits) ~ "BEBROAD: non-significant",
                                        p1 =="AN" & (p <= (0.05/n_traits)) ~ "AN: significant",
                                        p1 =="AN" & (p > (0.05/n_traits)) ~ "AN: non-significant"))

jacknife_rg_plotting %>% 
  freq(bonf_signif_plotting)
```

```{r factor relevel new names for plotting}
jacknife_rg_plotting <- jacknife_rg_plotting %>%
  mutate(bonf_signif_plotting = fct_relevel(bonf_signif_plotting,
                                   c("BEBROAD: significant",
                                     "BEBROAD: non-significant",
                                     "AN: significant",
                                     "AN: non-significant")))

jacknife_rg_plotting %>% 
  freq(bonf_signif_plotting)
```

```{r recode cateogries to numeric values}
jacknife_rg_plotting <- jacknife_rg_plotting %>%
  mutate(
    jn_diff_rg_stronger_AN_or_BEBROAD_numeric = 
      case_when(
        jn_diff_rg_stronger_AN_or_BEBROAD_plotting =="Both sig" ~ 4,
        jn_diff_rg_stronger_AN_or_BEBROAD_plotting == "Only BE BROAD sig" ~ 3,
        jn_diff_rg_stronger_AN_or_BEBROAD_plotting == "Only AN sig" ~ 3,
        jn_diff_rg_stronger_AN_or_BEBROAD_plotting =="BEBROAD rg > AN rg" ~ 2,
        jn_diff_rg_stronger_AN_or_BEBROAD_plotting =="AN rg > BE BROAD rg" ~ 1
      ))

# check
jacknife_rg_plotting %>%
  select(jn_diff_rg_stronger_AN_or_BEBROAD_numeric,
         jn_diff_rg_stronger_AN_or_BEBROAD_plotting,
         name)
  
```

# PLOT
## Try with facet wrap with two grid options instead of 1 to save text space in grid
recode categories to nice plotting names
```{r rename jn diff for plotting}
jacknife_rg_plotting <- jacknife_rg_plotting %>% 
  mutate(jn_diff_plotting =
           case_when(jn_diff == "rg jn same" ~"AN vs BE BROAD: No sig diff",
                     jn_diff == "rg jn different" ~"AN vs BE BROAD: Sig diff")
  )
```

```{r rg over 1 transform}
jacknife_rg_plotting <- jacknife_rg_plotting %>% 
  mutate(rg =
           case_when(rg > 1 ~ 1,
                     TRUE ~ rg))
```

```{r new dataset jn same}
plotting_jn_same <- jacknife_rg_plotting %>% 
  filter(jn_diff == "rg jn same")
```

Jacknife rg results significantly different
```{r new dataset jn different} 
plotting_jn_different <- jacknife_rg_plotting %>% 
  filter(jn_diff == "rg jn different")
```

Using facet_grid: Jacknife rg results the same
```{r plot jackknife same results}
rg_plot_facet_grid_jn_same_2_grid <- ggplot(data = plotting_jn_same,
       aes(x=reorder(reorder(name,
                     rg),
           jn_diff_rg_stronger_AN_or_BEBROAD_numeric),
           y=rg,
           color=bonf_signif_plotting,
           shape=bonf_signif_plotting)) +
  facet_grid(jn_diff_rg_stronger_AN_or_BEBROAD_plotting ~ jn_diff_plotting,
              scales = "free",
              space = "free") + 
  geom_point(position=position_dodge2(1),
             stat="identity",
             size=2.6) + # Width of rg estimate point
 geom_errorbar(aes(ymin=rg-se_rg,
                    ymax=rg+se_rg),
                width=.07,                    # Width of the error bars
                position=position_dodge(1),
                size=1)  +
  coord_flip(ylim=c(-0.6,1)) +
  labs(x = NULL,
       y = expression("Genetic correlation r"[g])) +
  scale_color_manual(values=c(
    "BEBROAD: significant" = "#D672A4", # colour by trait
    "AN: significant" = "#66B8BA",
    "BEBROAD: non-significant" = "#D672A4",
    "AN: non-significant" = "#66B8BA")) +
 scale_shape_manual(values=c("BEBROAD: significant" = 15,
                             "AN: significant" = 15,
                             "BEBROAD: non-significant" = 0,
                             "AN: non-significant" = 0)) + #hollow/filled square = 0/15, hollow/filled circle = 1/16, hollow/filled triangle = 2/1 
  geom_hline(yintercept=0,
              linetype="dashed",
              colour = "black",
              size = 1) +
  theme(legend.background = element_rect(fill=NA,
                                  size=0.2, 
                                  #linetype="solid",  #black box border around legend
                                  colour ="black"),
        panel.grid.major.y=element_line(size=.2,
                                          color="grey"),
        panel.grid.major.x = element_line(size=.2,
                                          color="grey" ),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(size=.5,
                                    color="grey",
                                    fill = NA),
        panel.background = element_blank(), 
        axis.line = element_blank(),
        axis.text.x = element_text(colour ="black"),
        axis.text.y = element_text(colour ="black"),
        axis.ticks.y = element_line(size=.2,
                                          color="grey"),
        axis.ticks.x = element_line(size=.2,
                                          color="grey"),
        legend.title = element_blank(),
        axis.text = element_text(size=17),
        text = element_text(size=17),
        legend.text = element_text(size = 16),
        legend.key = element_rect(fill = "white"),
        legend.key.size = unit(0.75, 'cm'),
        legend.key.height = unit(0.75, 'cm'), #change legend key height
        legend.key.width = unit(1.5, 'cm'),
        legend.position = "none",
        strip.text = element_text(size = 12)) +
  scale_y_continuous(n.breaks = 10)

```

Using facet_grid: Jacknife rg results significantly different
```{r plot jackknife different results}
rg_plot_facet_grid_jn_different_2_grid <- ggplot(data = plotting_jn_different,
       aes(x=reorder(reorder(name,
                     abs(rg)),
           jn_diff_rg_stronger_AN_or_BEBROAD_numeric),
           y=rg,
           color=bonf_signif_plotting,
           shape=bonf_signif_plotting)) +
  facet_grid(jn_diff_rg_stronger_AN_or_BEBROAD_plotting ~  jn_diff_plotting,
              scales = "free",
              space = "free") +
  geom_point(position=position_dodge2(1),
             stat="identity",
             size=2.6) + # Width of rg estimate point
 geom_errorbar(aes(ymin=rg-se_rg,
                    ymax=rg+se_rg),
                width=.07,                    # Width of the error bars
                position=position_dodge(1),
                size=1) +
  geom_vline(xintercept = 0, linetype = "longdash",size = 5, colour ="black") +
  coord_flip(ylim=c(-0.6,1)) +
  labs(x = NULL,
       y = expression("Genetic correlation r"[g])) +
  scale_color_manual(values=c(
    "BEBROAD: significant" = "#D672A4", # colour by trait
    "AN: significant" = "#66B8BA",
    "BEBROAD: non-significant" = "#D672A4",
    "AN: non-significant" = "#66B8BA")) +
 scale_shape_manual(values=c("BEBROAD: significant" = 15,
                             "AN: significant" = 15,
                             "BEBROAD: non-significant" = 0,
                             "AN: non-significant" = 0)) + #hollow/filled square = 0/15, hollow/filled circle = 1/16, hollow/filled triangle = 2/1 
   geom_hline(yintercept=0,
              linetype="dashed",
              colour = "black",
              size = 1) +
  theme(legend.background = element_blank(),
        panel.grid.major.y=element_line(size=.2,
                                          color="grey"),
        panel.grid.major.x = element_line(size=.2,
                                          color="grey" ),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(size=.5,
                                    color="grey",
                                    fill = NA),
        panel.background = element_blank(), 
        axis.line = element_blank(),
        axis.text.x = element_text(colour ="black"),
        axis.text.y = element_text(colour ="black"),
        axis.ticks.y = element_line(size=.2,
                                          color="grey"),
        axis.ticks.x = element_line(size=.2,
                                          color="grey"),
        legend.title = element_blank(),
        axis.text = element_text(size=17.5),
        text = element_text(size=17.5),
        legend.text = element_text(size = 17),
        legend.key = element_rect(fill = "white"),
        legend.key.size = unit(0.8, 'cm'),
        legend.key.height = unit(.6, 'cm'), #change legend key height
        legend.key.width = unit(1.2, 'cm'),
        legend.position = "top",
        strip.text = element_text(size = 13)) +
  scale_y_continuous(n.breaks = 10) +
  guides(color = guide_legend(nrow = 4))

```

```{r layout}
pp1_2_grid <- rg_plot_facet_grid_jn_same_2_grid
pp2_2_grid <- plot_spacer() / rg_plot_facet_grid_jn_different_2_grid + plot_layout(heights = c(1, 9))

pp1_2_grid + pp2_2_grid
```

# Save plot as pdf
```{r save plot pdf}
ggsave(filename = "AN_BEBROAD_1000DPI_largetxt_18_width2.pdf",
       path = "/Users/helenadavies/werk/PGC_ED_Freeze3/PGC_ED_F3_github_scripts/secondary_analysis_rg_results/",
       width = 20,
       height = 30,
       dpi = 1000
       ) 
```

# Save plot as png
```{r save plot png}
ggsave(filename = "AN_BEBROAD_1000DPI_largetxt_18_width2.png",
      path = "/Users/helenadavies/werk/PGC_ED_Freeze3/PGC_ED_F3_github_scripts/secondary_analysis_rg_results/",
        width = 20,
       height = 25,
       dpi = 1000
       ) 

```
