---
title: 'AN Plotting external rg: Single PGCED trait'
author: "Helena Davies"
date: "2023-07-14"
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

```{r load packages}
library(summarytools)
library(skimr)
library(gtsummary)
library(tidyverse)
```

# Read in and transform the results
## ANOREXIA NERVOSA
```{r Read in the data non MVP}
AN_rgs_non_MVP <- read_csv("/Users/helenadavies/werk/PGC_ED_Freeze3/PGC_ED_F3_github_scripts/secondary_analysis_rg_results/AN_PGCED3_rgs.csv")
```
# Keep correct traits in rg
```{r keep correct traits}
AN_rgs_non_MVP <- AN_rgs_non_MVP %>% 
  filter(p2 == "ADHD06" |
           p2 == "SMOK10" |
           p2 == "ALCD03" |
           p2 == "ALCU01" |
           p2 == "ALCU02" |
           p2 == "ALCU03" |
           p2 == "ALZH01" |
           p2 == "ANOR02" |
           p2 == "ANOR03" |
           p2 == "ANXI03" |
           p2 == "ASTH01" |
           p2 == "AUTI07" |
           p2 == "BALD01" |
           p2 == "BFPC03" |
           p2 == "BIPO03" |
           p2 == "BIPO04" |
           p2 == "BIPO05" |
           p2 == "BLOO01" |
           p2 == "BLOO02" |
           p2 == "BLOO03" |
           p2 == "BLOO04" |
           p2 == "BLOO05" |
           p2 == "BLOO06" |
           p2 == "BLOO07" |
           p2 == "BLOO08" |
           p2 == "BLOO09" |
           p2 == "BLOO10" |
           p2 == "BLOO11" |
           p2 == "BLOO12" |
           p2 == "BLOO13" |
           p2 == "BLOO14" |
           p2 == "BLOO15" |
           p2 == "BLOO16" |
           p2 == "BLOO17" |
           p2 == "BLOO18" |
           p2 == "BLOO19" |
           p2 == "BLOO20" |
           p2 == "BLOO21" |
           p2 == "BLOO22" |
           p2 == "BLOO23" |
           p2 == "BLOO24" |
           p2 == "BLOO25" |
           p2 == "BLOO26" |
           p2 == "BLOO27" |
           p2 == "BLOO28" |
           p2 == "BLOO29" |
           p2 == "BLOO30" |
           p2 == "BLOO31" |
           p2 == "BLOO32" |
           p2 == "BLOO33" |
           p2 == "BLOO34" |
           p2 == "BLOO35" |
           p2 == "BLOO36" |
           p2 == "BODY02" |
           p2 == "BODY04" |
           p2 == "BODY07" |
           p2 == "CANU02" |
           p2 == "CANU03" |
           p2 == "CAUD01" |
           p2 == "CELI01" |
           p2 == "CHOL21" |
           p2 == "CHOL22" |
           p2 == "CHOL27" |
           p2 == "CHRO01" |
           p2 == "CHRO02" |
           p2 == "CHRO06" |
           p2 == "SMOK09" |
           p2 == "CIRR01" |
           p2 == "COAD03" |
           p2 == "COLL01" |
           p2 == "CROH01" |
           p2 == "CROS01" |
           p2 == "DEPR02" |
           p2 == "DEPR05" |
           p2 == "DIAB02" |
           p2 == "ALCO04" |
           p2 == "EDUC02" |
           p2 == "EXTR01" |
           p2 == "FATM02" |
           p2 == "FATM02B" |
           p2 == "FATM02F" |
           p2 == "FATM02M" |
           p2 == "FATM03" |
           p2 == "FATM03B" |
           p2 == "FATM03F" |
           p2 == "FATM03M" |
           p2 == "FATM04" |
           p2 == "FATM04B" |
           p2 == "FATM04F" |
           p2 == "FATM04M" |
           p2 == "FATM05B" |
           p2 == "ANXI04" |
           p2 == "GLYC02" |
           p2 == "GLYC04" |
           p2 == "GLYC05" |
           p2 == "GLYC07" |
           p2 == "GLYC08" |
           p2 == "GLYC13" |
           p2 == "GLYC14" |
           p2 == "GLYC16" |
           p2 == "GLYC22" |
           p2 == "GROW01" |
           p2 == "GROW01F" |
           p2 == "GROW03" |
           p2 == "HEAD01" |
           p2 == "HEAL01" |
           p2 == "HEAR01" |
           p2 == "HEIG01" |
           p2 == "HEIG02" |
           p2 == "HEIG07" |
         #  p2 == "HEIG08" | using updated HEIG09
           p2 == "HIPC01" |
           p2 == "HIPC01F" |
           p2 == "HIPC01M" |
           p2 == "HIPC03" |
           p2 == "HIPC03F" |
           p2 == "HIPC03M" |
           p2 == "INCO01" |
           p2 == "INCO03" |
           p2 == "INFB01" |
         #  p2 == "INSO02" | using updated INSO03
           p2 == "INTE01" |
           p2 == "INTE03" |
           p2 == "LEAN02" |
           p2 == "LEAN03" |
           p2 == "LEAN04" |
           p2 == "LEAN04B" |
           p2 == "LEAN04F" |
           p2 == "LEAN04M" |
           p2 == "LEAN05" |
           p2 == "LEAN05B" |
           p2 == "LEAN05F" |
           p2 == "LEAN05M" |
           p2 == "LEAN06" |
           p2 == "LEAN06B" |
           p2 == "LEAN06F" |
           p2 == "LEAN06M" |
           p2 == "LEAN07B" |
           p2 == "LONG01" |
           p2 == "LONG02" |
           p2 == "LONG03" |
           p2 == "LONG04" |
           p2 == "LONG05" |
           p2 == "LONG06" |
           p2 == "LONG07" |
           p2 == "LUNG01" |
           p2 == "LUNG02" |
           p2 == "LUNG03" |
           p2 == "LUNG05" |
           p2 == "LUPU01" |
           p2 == "MEMO01" |
           p2 == "MENA03F" |
           p2 == "MENO01F" |
           p2 == "MIGR01" |
           p2 == "NEUR02B" |
           p2 == "OBES01" |
           p2 == "OBES02" |
           p2 == "OBES03" |
           p2 == "OBES05" |
           p2 == "OBES07" |
           p2 == "OCDI01" |
           p2 == "OSTE01" |
           p2 == "OSTE03" |
           p2 == "OSTE04" |
           p2 == "OSTE05" |
           p2 == "OVER01" |
           p2 == "ANXI05" |
           p2 == "PHYS01" |
           p2 == "PRCA01" |
           p2 == "PUTA01" |
           p2 == "REAC01" |
           p2 == "REAS01" |
           p2 == "REPR01" |
           p2 == "REPR01F" |
           p2 == "REPR01M" |
           p2 == "REPR02" |
           p2 == "REPR02F" |
           p2 == "REPR02M" |
           p2 == "RHEU02" |
           p2 == "RISK01" |
           p2 == "RISK02" |
           p2 == "RISK03" |
           p2 == "SCBP01" |
           p2 == "SCBP02" |
           p2 == "SCHI05" |
           p2 == "SMOK05" |
           p2 == "SMOK08" |
           p2 == "SMOK07" |
           p2 == "SUBJ01" |
           p2 == "THIN01" |
           p2 == "TIRE01" |
           p2 == "TOUR01" |
           p2 == "TRGL04" |
           p2 == "URAT01" |
           p2 == "URIN08" |
           p2 == "URIN11" |
           p2 == "VITD01" |
           p2 == "WAIS01F" |
           p2 == "WAIS01M" |
           p2 == "WAIS03" |
           p2 == "WAIS03F" |
           p2 == "WAIS03M" |
           p2 == "WEIG01" |
           p2 == "WEIG04F" |
           p2 == "WEIG04M" |
           p2 == "WEIG05F" |
           p2 == "WHIP01" |
           p2 == "WHIP03" |
           p2 == "WHIP03F" |
           p2 == "WHIP03M" |
           p2 == "WHIP05" |
           p2 == "WHIP05F" |
           p2 == "WHIP05M" |
           p2 == "BODY04F" |
           p2 == "BODY04M" |
           p2 == "EDUC03" |
           p2 == "HEIG09" |
           p2 == "CROS01" |
           p2 == "PSOR01" |
           p2 == "SMOK11" |
           p2 == "INSO03" |
           p2 == "ADHD06" |
           p2 == "SMOK10" |
           p2 == "BIPO03" |
           p2 == "BIPO04" |
           p2 == "BIPO05" |
           p2 == "CANU02" |
           p2 == "CANU03" |
           p2 == "SMOK09" |
           p2 == "ALCO04" |
           p2 == "SMOK08" |
           p2 == "SMOK07" |
           p2 == "ANXI05" |
           p2 == "TOUR01" |
           p2 == "LONE04" |
           p2 == "BODY15" |
           p2 == "GLYC47" |
           p2 == "GLYC48" |
           p2 == "GLYC49" |
           p2 == "GLYC48F" |
           p2 == "GLYC48M" |
           p2 == "GLYC50" |
           p2 == "GLYC51" |
           p2 == "GLYC50F" |
           p2 == "GLYC50M" |
          # p2 == "GLYC52" | USING glyc22 as bigger h2
           p2 == "GLYC53" |
           p2 == "REPR04" |
           p2 == "REPR03")
```

```{r Read in the data MVP}
AN_rgs_MVP <- read_csv("/Users/helenadavies/werk/PGC_ED_Freeze3/PGC_ED_F3_github_scripts/secondary_analysis_rg_results/AN_PGCED3_MVP_rgs_MVP.csv")
```

```{r bind MVP and non MVP}
AN_rgs <- AN_rgs_MVP %>%
  bind_rows(AN_rgs_non_MVP)
```

```{r see missing}
AN_rgs %>%
  filter(is.na(rg))
```

Merge with GWAS information sheet to get phenotype name for plotting (and PMID, year, etc)
```{r merge with GWAS info}
trait_details <- read_csv(file = "/Users/helenadavies/Downloads/PGC ED GWAS rg analyses - RULES APPLIED_ PGC-ED rg traits (9).csv")

trait_details <- trait_details %>% 
  select(p2 = "KCL code", # rename Code to p2 so that it matches with column name in rg results
         name,
         name_plotting,
         Phenotype_category,
         category_name
         ) 

AN_rgs_results_details <- left_join(AN_rgs,
                                 trait_details,
                                 by = "p2")

AN_rgs_results_details

## for now ##
AN_rgs_results_details <- AN_rgs_results_details %>%
  mutate(name =
           case_when(!is.na(name_plotting) ~ name_plotting,
                     TRUE ~ name))
```

Specify number of traits used for genetic correlation to correct for multiple testing using Bonferonni 
```{r no. traits}
n_traits <- nrow(AN_rgs_results_details)
```

Create column to specify if significant for trait 1 or trait 2 or trait 3 (or both)
```{r}
AN_rgs_results_details <- AN_rgs_results_details %>%
  mutate(bonf_signif =
           case_when((p < (0.05/n_traits)) ~ "significant",
                     (p >= (0.05/n_traits)) ~ "non-significant"))

AN_rgs_results_details %>%
  count(bonf_signif)
```
Save for supplementary table
```{r save table for supplementary}
AN_rgs_results_details <- AN_rgs_results_details %>%
  filter(!is.na(rg)) %>%
  select(
    Trait = name,
    'Category' = category_name,
    rg,
    SE = se,
    p,
    'Bonferroni significant' = bonf_signif
    )

AN_rgs_results_details_ordered <- AN_rgs_results_details[order(AN_rgs_results_details$Category), ]

write_excel_csv(AN_rgs_results_details_ordered,
                file = "/Users/helenadavies/werk/PGC_ED_Freeze3/PGC_ED_F3_github_scripts/secondary_analysis_rg_results/single_trait_rg/AN_PGCED3_rgs_SUPPLEMENTARY2.csv")
``` 

# Plot: order by strength of rg
Filter for only significant rg for plotting
```{r filter sig rg only plotting}
AN_rgs_results_details_sig <- AN_rgs_results_details %>%
  filter(`Bonferroni significant` == "significant")
```

Create column to specify if negative or positive for plotting
```{r direction of rg}
AN_rgs_results_details_sig <- AN_rgs_results_details_sig %>%
  mutate(direction =
           case_when(rg > 0 ~ "positive",
                     rg < 0 ~ "negative"))

AN_rgs_results_details_sig %>%
  count(direction)
```

Set preferences for text size and style 
https://htmlcolorcodes.com/color-picker/
```{r set text prefs}

black_bold_italic_text <- element_text(face = "bold.italic",
                                      color = "black",
                                      size = 25)

black_bold_text <- element_text(face = "bold",
                                colour = "black",
                                size = 30)


black_plain_text <- element_text(face = "plain",
                           colour = "black",
                           size = 25)

black_plain_text_smaller <- element_text(face = "plain",
                           colour = "black",
                           size = 20)


## Set preferences for ggplot theme
my_theme <- theme(title = black_bold_text,
                  plot.subtitle = black_bold_italic_text,
                  axis.title.x = black_plain_text,
                  axis.title.y = black_plain_text,
                  axis.text = black_plain_text_smaller) 
```

Run ggplot
```{r Plot genetic correlations}
plot <- ggplot(AN_rgs_results_details_sig,
       aes(x=Trait,
           y=rg,
          color=direction
           )) + 
  geom_point(position=position_dodge2(1),
             stat="identity",
             size=5) +
     geom_hline(yintercept=0,
              linetype="dashed",
              colour = "black",
              size = 1) +
 coord_flip(ylim=c(-1,1.2)) +
  labs(title = "Anorexia nervosa",
    x = "External trait",
    y = expression("Genetic correlation r"[g])) + # Width of rg estimate point
  geom_errorbar(aes(ymin=rg-SE,
                    ymax=rg+SE),
                width=.1,                    # Width of the error bars
                position=position_dodge(1),
                size=1) +
  scale_color_manual(values=(c("positive" = "#6DA553",
                             "negative" = "#F15E58"))) + # colour by direction
  theme(panel.grid.major.y=element_line(size=.2,
                                          color="black" ),
        panel.grid.major.x = element_line(size=.2,
                                          color="black" ),
         panel.grid.minor = element_blank(),
        panel.border = element_rect(size=.5,
                                    color="grey",
                                    fill = NA),
        panel.background = element_blank(), 
        axis.line = element_blank(),
        axis.text.x = element_text(colour ="black"),
        axis.text.y = element_text(colour ="black",
                                   size = 22),
        axis.ticks.y = element_line(size=.2,
                                          color="grey"),
        axis.ticks.x = element_line(size=.2,
                                          color="grey"),
        axis.text = element_text(size=17),
        axis.title.y = element_text(size=30),
        title = element_text(size=30),
        text = element_text(size=17),
        strip.text = element_text(size = 20,
                                  colour="black",
                                    face = "bold"),
        strip.background =element_rect(fill="light grey"),
      legend.position = "none") + 
    # my_theme +
    facet_grid(vars(Category), scales="free_y", space="free")+
  theme(strip.text.y = element_text(angle=0),
        panel.border = element_rect(color = "black", fill = NA, size = 1),
        panel.spacing = unit(1, "lines"),
                strip.background = element_rect(color = "black", size = 1))
```

Save rg plot
```{r Save rg plot}
ggsave(filename = "/Users/helenadavies/werk/PGC_ED_Freeze3/PGC_ED_F3_github_scripts/secondary_analysis_rg_results/single_trait_rg/AN_PGCED3_rgs_plot2.png",
       plot = plot,
       height = 65,
       width = 50,
       units = "cm",
       device = "png")
```


