---
title: "Make nice plotting names column"
author: "Abigail ter Kuile"
date: "2022-12-23"
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

```{r load packages}
library(summarytools)
library(skimr)
library(gtsummary)
library(tidyverse)
```

```{r Source the credentials file}
source("credentials/paths.R")
```

# Read in results that need nice plotting names 
```{r}
results_gad_fear <- read_csv(file = paste0(path_anxiety_gwas,
                              "results/meta/external_rg/long_abstract/gad_fear_rg_results_all_gwas_info_NEW_COLUMNS.csv"))

```

```{r}
results_gad_fear <- results_gad_fear %>% 
  mutate(plotting_name = name)
```

# save
```{r}
write_excel_csv(results_gad_fear,
                file = paste0(path_anxiety_gwas,
                              "results/meta/external_rg/long_abstract/gad_fear_rg_results_all_gwas_info_add_to_plotting_name.csv"))

```

# Read in results that now have nice plotting names (manually edited and added)
```{r}
results_gad_fear_plotting_names_added <- read_csv(file = paste0(path_anxiety_gwas,
                              "results/meta/external_rg/long_abstract/EDIT_THIS_plotting_names_added_gad_fear_rg_results_all_gwas_info.csv"))

results_gad_fear_plotting_names_added_limited_col <- results_gad_fear_plotting_names_added %>% 
  select(p2,
         plotting_name,
         keep_for_plotting)
```

Drop duplicates
```{r}

results_gad_fear_plotting_names_added_limited_col_nodups <- results_gad_fear_plotting_names_added_limited_col %>%
 distinct(p2, plotting_name, .keep_all= TRUE)
```

# Merge with GWAS information sheet to add new column for plotting
```{r}
trait_details <- read_csv(file = paste0(path_anxiety_gwas,
                                        "results/meta/external_rg/long_abstract/sumstats_list_all_info_221222.csv"))

trait_details <- trait_details %>% 
  rename(p2 = code) #rename Code to p2 (phenotype 2 from rg results)

```
```{r}
rgs_results_details_plotting <- left_join(trait_details,
                                 results_gad_fear_plotting_names_added_limited_col_nodups,
                                 by = "p2")

glimpse(rgs_results_details_plotting)
```

```{r}
rgs_results_details_plotting <- rgs_results_details_plotting %>%
  mutate(plotting_name_all =
           case_when(
             (is.na(plotting_name)) ~ name,
             (!is.na(plotting_name) ~ plotting_name
              )
                     ))
```

```{r}
rgs_results_details_plotting <- rgs_results_details_plotting %>% 
  rename(code = p2)
```

# Save
"results/meta/external_rg/long_abstract/sumstats_list_all_info_221222.csv"
```{r}
write_excel_csv(rgs_results_details_plotting,
                file = paste0(path_anxiety_gwas,
                              "results/meta/external_rg/long_abstract/anx_paper_plotting_names_sumstats_list_all_info_1222.csv"))

```


